The impacts of public health policy measures on reducing SARS-CoV-2 transmission in Australia

### 2020-05-17 manuscript/ms.Rmd
add text and tables on parameter values

@@

\begin{align}
  D_t &= e^{\beta d_t}
\end{align}

@@

\begin{equation}
 Q_t = \begin{cases}
  q1 & t < \tau_1 \\
  q2 & \tau_1 \leq t < \tau_2 \\
  q3 & \tau_2 \leq t
 \end{cases}
\end{equation}

where $q1 > q2 > q3$ and all parameters are constrained to the unit interval.

@@

\begin{align}
  \epsilon_i^L &\sim GP(\mathbf{0}, k^L(t, t')) \\
  k^L(t, t') &= k_{SE}(t, t') + k_{RQ}(t, t') + k_{IID}^L(t, t') \\
  k_{SE}(t, t') &= \sigma_1^2 \, exp \left( -\frac{(t - t')^2}{2 l_1^2} \right) \\
  k_{RQ}(t, t') &= \sigma_2^2 \, exp \left(1 + \frac{(t - t')^2}{2 \alpha l_1^2} \right)^{-\alpha} \\
  k_{IID}^L(t, t') &= \begin{cases}
    \sigma_3^2 & t = t' \\ 
    0 & t \neq t'
 \end{cases}
\end{align}

@@

>>>>

```{r setup, echo = FALSE, message = FALSE}
library(dplyr)
```

@@

\begin{align}
  D_t &= 1 - \beta d_t
\end{align}

@@

\begin{equation}
 Q_t = \begin{cases}
  q_1 & t < \tau_1 \\
  q_2 & \tau_1 \leq t < \tau_2 \\
  q_3 & \tau_2 \leq t
 \end{cases}
\end{equation}

where $q_1 > q_2 > q_3$ and all parameters are constrained to the unit interval.

@@

\begin{align}
  \epsilon_i^L &\sim GP(\mathbf{0}, k^L(t, t')) \\
  k^L(t, t') &= k_{SE}(t, t') + k_{RQ}(t, t') + k_{IID}^L(t, t') \\
  k_{SE}(t, t') &= \sigma_1^2 \, exp \left( -\frac{(t - t')^2}{2 l_1^2} \right) \\
  k_{RQ}(t, t') &= \sigma_2^2 \, exp \left(1 + \frac{(t - t')^2}{2 \alpha l_2^2} \right)^{-\alpha} \\
  k_{IID}^L(t, t') &= \begin{cases}
    \sigma_3^2 & t = t' \\ 
    0 & t \neq t'
 \end{cases}
\end{align}

@@

### Parameters and priors

Tables \@ref(tab:mechanistic_priors) and \@ref(tab:timeseries_priors) give the prior distributions of parameters in the semi-mechanistic and timeseries ($\epsilon^L$ and $\epsilon^O$) parts of the model respectively. Table \@ref(tab:mechanistic_parameters) gives fixed parameter values usedin the semi-mechanistic part of the model.

The parameters of the generation interval distribution are the posterior means of the lognormal distribution over the serial interval estimated by Nishiura et al. (2020).

The parameters of lognormal prior over $R_0$ were computed such that the distribution matched the averages of the posterior means and 95% credible intervals for 11 European countries as estimated by Flaxman et al. (2020) (Imperial College report 13) in a sensitivity analysis where the mean generation interval was 5 days - similar to the serial interval distribution assumed here. This corresponds to a prior mean of 2.79, and a standard deviation of 1.70.

We assumed slightly informative priors over the lengthscales of components 2 and 3 of the timeseries over R effective for local-local transmission (parameters $l_1$ and $l_2$), such that longer lengthscales were more likely for component 2 (timeseries of the state-wide average transmission rate) than for component 3 (timeseries of the average transmission rate over active cases).

```{r mechanistic_priors, echo = FALSE}
tibble::tribble(

  ~"Prior distribution",
  ~"Parameter description",

  "$R_0 \\sim \\mathrm{lognormal}(1.02, 0.10^2)$",
  "Basic reproduction number",

  "$\\beta \\sim \\mathrm{U}(0, 1)$",
  "Effect of social distancing behaviours",

  "$q_1 \\sim \\mathrm{U}(0, 1)$",
  "Effect of quarantine of overseas arrivals (phase 1)",

  "$q_2 / q_1 \\sim \\mathrm{U}(0, 1)$",
  "Relative effect of quarantine (phase 2 vs 1)",

  "$q_3 / q_2 \\sim \\mathrm{U}(0, 1)$",
  "Relative effect of quarantine (phase 3 vs 2)"

) %>%
  knitr::kable(caption = "Prior distributions for parameters in the semi-mechanistic part of the time-varying model of $R_eff$", escape = FALSE)
```

```{r mechanistic_parameters, echo = FALSE}
tibble::tribble(

  ~"Parameter value",
  ~"Parameter description",

  "$\\tau_1$ = 2020-03-15",
  "Date of change from overseas quarantine policy phase 1 to 2",

  "$\\tau_2$ = 2020-03-28",
  "Date of change from overseas quarantine policy phase 2 to 3",

  "$g(t) = \\int_{t-1}^{t} \\mathrm{lognormal}(t | 1.377, 0.567^2) \\mathrm{d}t$",
  "Generation interval function",

) %>%
  knitr::kable(caption = "Values of fixed parameters in the semi-mechanistic part of the time-varying model of $R_eff$", escape = FALSE)
```

```{r timeseries_priors, echo = FALSE}
tibble::tribble(

  ~"Prior distribution",
  ~"Parameter description",

  "$\\sigma_1 \\sim \\mathrm{N}^+(0, 0.25^2)$",
  "Amplitude of deviation; local $R_{eff}$ statewide",

  "$l_1 \\sim \\mathrm{lognormal}(4, 0.5^2)$",
  "Temporal correlation; local $R_{eff}$ statewide",

  "$\\sigma_2 \\sim \\mathrm{N}^+(0, 0.25^2)$",
  "Amplitude of deviation; local $R_{eff}$ active cases",

  "$l_2 \\sim \\mathrm{lognormal}(2, 0.5^2)$",
  "Temporal correlation; local $R_{eff}$ active cases",

  "$\\alpha\\sim \\mathrm{lognormal}(2, 0.5^2)$",
  "Correlation mixture weights; local $R_{eff}$ active cases",

  "$\\sigma_3 \\sim \\mathrm{N}^+(0, 0.25^2)$",
  "Overdispersion; local $R_{eff}$ active cases",

  "$\\sigma_4 \\sim \\mathrm{N}^+(0, 0.5^2)$",
  "Amplitude of deviation; import $R_{eff}$ statewide",

  "$\\sigma_5\\sim \\mathrm{N}^+(0, 0.5^2)$",
  "Overdispersion; import $R_{eff}$ active cases",

) %>%
  knitr::kable(caption = "Prior distributions for parameters used in the timeseries part of the time-varying model of $R_eff$", escape = FALSE)
```
